Unified Convergence Analysis of FedAve on Non-IID Data

### 2020-05-25 source/main.tex
add stronlgy convex and convex smooth results

% \tableofcontents
\begin{abstract}
Federated learning is a distributed learning paradigm that enables learning a
model jointly over a large number of workers without sharing the private data
on local workers. The characteristics of non-identically distributed data
across the network and low device participation bring significant challenges
in analyzing the convergence of federated learning algorithms. Prior works
mainly analyze its convergence rate in limited scenarios.
In this work, we provide a comprehensive analysis of the convergence rate of SGD and Nesterov SGD for general convex problems.
Theoretically, we firstly show 
that the convergence rates enjoy a linear speedup for
all convex smooth problems for both algorithms.
Furthermore, we propose a new accelerated SGD algorithm improving the convergence rate over SGD in the overparameterized setting. 
Empirical evaluation of the algorithms in various settings match our theoretical
results.
\end{abstract}

@@

% accelerated 
% convex strongly 
% smooth non-smooth. 
\input{sec_problem}
\input{sec_theorems}
\newpage
\input{sec_exp}
\input{sec_exp_note}

>>>>

% \tableofcontents
\begin{abstract}
Federated learning is a distributed learning paradigm that enables learning a
model jointly over a large number of workers without sharing the private data
on local workers. The characteristics of non-identically distributed data
across the network and low device participation bring significant challenges
in analyzing the convergence of federated learning algorithms. Prior works
have either analyzed the convergence with i.i.d. data, or with full device
participation, and often with suboptimal rates. In this work, we provide a
comprehensive analysis of the convergence rate of Federated Averaging (FedAvg)
with SGD and Nesterov SGD updates for general convex problems with arbitrarily
heterogeneous data. Firstly we show that the convergence rates enjoy a linear
speedup in the number of participating workers for all convex smooth problems
for both algorithms. Furthermore, we propose a new accelerated federated
learning algorithm improving the convergence rate over FedAvg with SGD in the
overparameterized setting. Empirical evaluation of the algorithms in various
settings match our theoretical results.
\end{abstract}

@@

% accelerated 
% convex strongly 
% smooth non-smooth. 
\input{sec_problem}
\input{sec_theorems}
\newpage
\input{sec_exp}
% \input{sec_exp_note}

### 2020-05-25 source/sec_exp.tex
add stronlgy convex and convex smooth results

\begin{figure}[h!]
\centering
\begin{tabular}{cc}
	\includegraphics[width=0.5\textwidth]{fig/E1-4-16speedupNodesT-min-w8a-epsilon013-b4-reg1e-05-adapt0.pdf} & 
\includegraphics[width=0.5\textwidth]{fig/E1-4-16speedupEpochsT-min-w8a-epsilon013-b4-reg1e-05-adapt0.pdf} 
\end{tabular}
	\caption{Logistic regression with regularization $1e-5$. The linear speed up w.r.t the number of nodes and number of epochs. The synthetic dataset has $N=49749$ samples, evenly distributed on $1, 2, 4, 8, 16, 32, 64, 128, 256, 512, 1024$ devices. The figure shows the number of iterations/rounds needed to converge to $\epsilon-$accuracy. The learning rate is decayed as the $\eta_t = \min(32, \frac{Nc}{1 + t})$, where we extensively search the best learning rate $c \in \{2^{-1}c, 2^{-2}c, c, 2c, 2^{2}c\}$ and for each configuration. Batch size is 4 in this case.}
\end{figure}

@@

>>>>

\begin{figure}[h!]
\centering
\begin{tabular}{cc}
	\includegraphics[width=0.45\textwidth]{fig/paper-stronglycvxsmthspeedupNodesT-min-w8a-epsilon0131-reg1e-05.pdf} & 
\includegraphics[width=0.45\textwidth]{fig/paper-stronglycvxsmthspeedupEpochsT-min-w8a-epsilon0131-reg1e-05.pdf} \\
\end{tabular}
	\caption{Logistic regression with regularization $1e-5$. The linear speed up w.r.t the number of nodes and number of epochs. The synthetic dataset has $N=49749$ samples, evenly distributed on $1, 2, 4, 8, 16, 32$ devices. The figure shows the number of iterations/rounds needed to converge to $\epsilon-$accuracy, where $\epsilon=0.005$. The learning rate is decayed as the $\eta_t = \min(32, \frac{Nc}{1 + t})$, where we extensively search the best learning rate $c \in \{2^{-1}c, 2^{-2}c, c, 2c, 2^{2}c\}$ and for each configuration. Batch size is 4 in this case.}
\end{figure}

@@

\begin{figure}[h!]
\centering
\begin{tabular}{cc}
	\includegraphics[width=0.45\textwidth]{fig/paper-cvxsmoothspeedupNodesT-min-w8a-epsilon013-b4-reg0.pdf} & 
\includegraphics[width=0.45\textwidth]{fig/paper-cvxsmoothspeedupEpochsT-min-w8a-epsilon013-b4-reg0.pdf} \\
\end{tabular}
	\caption{Logistic regression without regularization. The linear speed up w.r.t the number of nodes and number of epochs. The w8a dataset has $N=49749$ samples, evenly distributed on $1, 2, 4, 8, 16, 32, 64, 128, 256, 512, 1024$ devices. The figure shows the number of iterations needed to converge to $\epsilon-$accuracy, where $\epsilon=0.02$. The learning rate is decayed as the $\eta_t = \min(\eta_0, \frac{Nc}{1 + t})$, where we extensively search the best learning rate $c \in \{2^{-1}c, 2^{-2}c, c, 2c, 2^{2}c\}$, $\eta_0 \in \{1, 32\}$ and for each configuration. Batch size is 4 in this case.}
\end{figure}
